---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# broadcasteR

<!-- badges: start -->
<!-- badges: end -->

This package encapsulates many different utility functions for analyzing TV ratings and metrics. There are two major sections to this package: media, and other. The media functions all relate to and calculate Nielsen formulas, whereas other functions are a random smattering of utilities.

## Installation

You can install the development version of broadcasteR like so:

``` {r install, echo = T, results = 'hide', message = F, warning = F, eval = F}

devtools::install_github("syrchanan/broadcasteR")

```

## Example

This is a basic example which shows you how to use any of the `media_` utility function.

Call a function with the `media_` prefix, then leave the target metric as an NA value, and fill in all the others.

Below is an example calculation of AA rating from UE and AA.

```{r example, eval = F}

# Load the library
library(broadcasteR)

media_aa_1(rating = NA, ue = 1000, aa = 200)

```
